Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-05-07 hpmoon-asoco.tex
Removed 3rd person references

\begin{bluecolor}

@@

%%%NEW AND SHORTED
Parallel island-model co-evolutionary algorithms are well-known methods, suitable for dealing with large multi-objective optimization problems. In these algorithms, each island modifies a fragment of the chromosome that encodes a possible solution to the problem. In this paper, we want to demonstrate that automatically setting the size of the overlapping fragments depending on the number of islands obtains better results than using the same size. We  have compared this method to other parallel evolutionary techniques considering a different number of islands, chromosome sizes and benchmarks. The analysis of the obtained experimental results, by using different metrics, shows that our approach can provide statistically significant improvements with respect to the base algorithm in high-dimensional, un-decomposable, multi-objective problems. This opens a very promising line to automatically adapt the overlapping sizes in this kind of algorithms.

\end{bluecolor}

@@

In our previous work \citep{Garcia16hpmoon} we used this method in a
preliminary experimental setup, although it is worth mentioning we are
establishing its name and acronym in this paper for the first time.
We show
that applying the variation operators only over specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
Moreover, instead of making every island focus on a disjoint subset of the
chromosome, the usage of overlapped (shared) sections of the
chromosome 
can improve the quality of the solutions 
when the number of islands is increased. In that paper, we showed that the most
adequate overlapping size may vary depending on a relation between the
number of islands and the individual size. However, it was a proof-of-concept, and the experiments
were conducted in a limited experimental system: mono-processor and
synchronous island model. 
This
motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more \textcolor{blue}{extensive parameter evaluation}. Besides comparing previous methods in this new experimental setup, in this paper we propose
a new method that automatically sets the size of the overlapped
sections depending on the number of available islands, comparing it with previous versions.

@@

The approach described by Dorronsoro et al. has also been used by Kimovski et al. \citep{Kimovski15Parallel}, but implementing a
master-slave method that splits the population into several processors. As in previous works, each node
runs a parallel MOEA that only affects some portion of 
the individuals and the master
process receives all the sub-populations to be combined every certain number of generations. Up to 8 processors
were used in the experimental setup, and several
combination alternatives were compared. The main difference of our work with respect to previous works is that our approach does not 
broadcast all solutions to all islands for recombination, but only one solution to a random island, needing less
communication time. Moreover, Dorronsoro or Kimovsky approaches limited the maximum number of islands to 8, while in this paper we have
used up to 128 islands.

@@

In our previous work \citep{Garcia16hpmoon} we used some of
the aforementioned ideas to compare two different dMOEAs. The first
one divided the chromosome into $P$ sections,  $P$ being the number of
islands. Every island $p$ only performed the mutation and crossover in
that part ($p_{th}$) of the chromosome (the selective operator application), while the fitness was
calculated using the whole individual. After a certain number of
generations, individuals were migrated randomly to other islands. The
performance metrics were calculated at the end of the run. The second
method, selective operator application with overlapping islands, used the $p_{th-1}$ and
$p_{th+1}$ sections of each chromosome, besides the $p_{th}$
part. During the same amount of time, both methods obtained better
results than a baseline algorithm that dealt with the whole chromosome
in each island for crossover and mutation. We discovered that the
performance using one or another method depends on the number of
sections of the individuals and the number of islands used. This
motivated us to find a new automatic method to select this number of
sections of the chromosome to use, depending on the number of
islands. Besides, previous experiments were performed on a single
processor synchronous island model with a limited number of islands
(8, 32 and 128). In this paper,  8, 16, 32, 64 and 128 islands have
been used, and on this occasion, the experiments have been run on a parallel
cluster. 
Therefore, at the same time, we are proposing a new method to divide the individual search space according to the number of evolved subpopulations, and also validating the previous approach.

We will describe how we have tested our approach in the next Section.

@@

The objective of this section is to explain the methodology we have followed to
compare the different versions of the overlapping schemes.

\subsection{Proposed methods}
In this paper we analyze several SLA algorithms we have
implemented by using a parallel multi-objective baseline algorithm
as a basis for comparisons. Our proposed methods, using different overlapping schemes, 
are based on NSGA-II, as almost all the previous works discussed
before
\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Deb03distributed,Xiao03specialized,Wang09parallel,Martens13asynchronous}. 
Therefore, we have used a basic distributed NSGA-II algorithm without
overlapping sections as the baseline (B).

This basic distributed algorithm spreads the population among $P$
islands; after a fixed number of generations,
one individual in a given island is migrated to another random island,
thus avoiding to synchronize the global PF every
certain number of generations as other methods described in Section 2
do. At the end of the run, the PFs of all islands are
aggregated into a new one, and the quality measures are evaluated. 
Different  SLA alternatives can be devised to evolve the
subpopulations according to the decision space to be explored by each
island. Here we will consider three methods in which each island only
performs crossover and mutation in specific sections of the
individuals.

@@

The methods we have tested are presented in the next subsections.

@@

As a first
approach to automatically calculate this value, the results shown in
\citep{Garcia16hpmoon} have been used as a base to obtain $c$. In that
work, the overlapped method ($c=1$) obtained better results when the
number of islands was bigger than 8. On the contrary, when the number of
islands is small, no overlapping is necessary. So, we have used this
knowledge to propose the formula $c=round(0.2*P-1)/2$ to calculate the
extra sections to overlap. Therefore, when $P=8$ then $c=0$
(equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so
on. Dividing individuals by blocks of equal size, instead of a percentage, allow the future integration of our method with other recombination mechanisms, such as the ones presented in \cite{Dorronsoro13superlinear} or \cite{Kimovski15Parallel}.
Also, as mentioned, this is only a possible formula to reach above-described behaviour for $c$, and future work will study new methods or alternative formulas to determine it, for example using Taguchi Method \cite{Keratmatpour2018Taguchi}.  Figure \ref{fig:adaptive} explains the $A$ method, assuming that $c=2$, for example.

@@

We have chosen those metrics not only because they have been used
extensively, especially in some of the papers presented in Section \ref{sec:soa}
\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous},
but also because they cover different quality criteria. Mathematical
formulation of these metrics can be found in
\cite{Dorronsoro13superlinear}.

@@

The global population size is set to 1024. We have decided to use that value for two reasons: the first is that it is large enough to have 8 individuals per island by dividing that number when using 128 islands and small enough to have 128 individuals when using 8 islands. This is the minimum and maximum population size per island used by M{\"a}rtens et al. in his work \cite{Martens13asynchronous}.

The criterion used for terminating an experiment has been the running
time: 25 seconds for dimension 512 and 100s (four times more) for
2048. According to Alba and Luque \cite{EVALUATIONPARALLEL}, other stop criteria such as the number of evaluations required to attain a solution, may be misleading depending on the studied scenario. In our case, we have used time instead of the number of evaluations firstly
because our hypothesis argues that the time saved in crossover and
mutation can be spent on improving the sub-populations and more
operations and migrations can be achieved. Also, we are using
different numbers of islands (with different sub-population sizes) and that
could lead to different execution times, so it would be difficult to
compare different times and quality of solutions at the same time.

The number of generations between migrations has been set to 5,
as
reported by \cite{Deb03distributed,Martens13asynchronous}. In general
and as affirmed by 
\cite{cantu1998survey}, this migration gap has contradictory effects
on the result: by increasing it, we make the system closer to a
single-node one, since populations tend to mix without restriction; by
decreasing it, we make the isolate islands more prone to being stuck
in local minima. \cite{Martens13asynchronous} mentions that several
values were tested with no influence in the result; in our particular
case, the mixing is essential for the algorithm to spread the result
to all parts of the chromosome. So, while we tend to agree with
M{\"a}rtens on the small influence of this value on the result, we also
think that making this value much bigger in our case would have a
negative impact. However, a precise fine-tuning of this value is left
as future work, as the main focus of this paper was to show the
general concept, and not tune the values for maximum performance.

@@

calculated (see Figure \ref{fig:hypervolume}), we have chosen the value (1,9) as none of the existing solutions on all fronts obtained during all executions are dominated by it. In other words, as we are minimizing in both objectives, this reference point is required to be numerically larger or equal in each objective, and strictly larger in at least one of them (dominated) for all solutions in the PFs we are going to measure. HV is then

@@

The average results for each configuration are shown in
Table \ref{tab:results512} (for 512 dimensions) and Table
\ref{tab:results2048} (for 2048). As previously explained, when $P=8$
the results of A are equivalent to the obtained by D (because
$c=0$), and when $P=16$ they are equivalent to O ($c=1$). We refer this equivalence with the word {\em Equiv-} in tables. For example, Equiv-D in an HV cell  means that the HV of A is the same than the value in D column, because the behaviour of this configuration is the same than executing D.

@@

%%%%%%FERGU: WARNING, THIS SECTION IS STILL SHIT
%ZDT1 
After establishing the performance of the new method and in order to
have some insight on how they work, the effect of the different chromosome sizes and number of
islands can be checked. Plotting the solution sets allows to observe its quality, distribution and shape, specially if they are limited to 2 or 3 objectives, as in this paper \cite{Li17read}.  Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048} show the
final PFs of one arbitrary sample run of each combination;. The first
one, ZDT1, has a convex Pareto-optimal front. Comparing results from
$L=512$ (Figure \ref{fig:plot_zdt1_512}) and $L=2048$ (Figure
\ref{fig:plot_zdt1_2048}) it is apparent that the quality of the
generated PFs depends on the chromosome size. Specifically, all
configurations  with
$L=512$  seem to have a worse Spread and HV, on the other hand, the
SLA methods behave worse than $B$, as it was also shown on average in
Table \ref{tab:results512}. Nevertheless, if we focus on the plots
obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this
difference is less clear. Figure \ref{fig:plot_zdt1_2048} shows that
solutions obtained by the SLA methods show higher dispersion than the
baseline as $P$ grows. However, with $A$, the area covered by the PF
is still larger.

@@

In ZDT6, the Pareto-optimal solutions are not only non-uniformly distributed along the PF, but their density also increases as we move further away from it. That is the reason why some PFs obtained have an extremely low number of solutions in some configurations, and also, they are aggregated toward the areas with more density. Moreover, all configurations, including $B$, obtained PFs relatively far away from the optimal PF, as opposed as in previous problems. Spread is very similar for all methods $B$, $D$, $O$, $A$ across different $L$ sizes. Indeed, there is not a significant difference between methods, with an exception: Spread using $A$ with $L=512$ is significantly worse. As in previous approaches, it is visually clear that increasing the number of islands, and therefore, reducing the number of individuals per island, implies a decrease the in quality of the HV.

@@

Obtained results also show that when increasing the number of islands, the
automatic overlapping method ($A$) significantly improves the results with
respect to the disjoint and overlapped methods. However, this is only
apparent with larger chromosome sizes. Therefore, the length of the
chromosome is also a key factor to take into account in automatic overlapping
methods, and not only the number of islands. 
%Studying this factor with more types of problems, and new configurations of population size and chromosome lengths could be addressed in the future. 
Since our method divides the individuals into blocks of divisible size, aggregation methods after migration, such as the ones used in \cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be also tested. But as we are dealing with complete individuals in each island, the possibility of using a real number, such as 0.3 (30\% overlapping) instead an integer value opens future experimental setups.
For example, comparing 
different ways to calculate $c$ using linear, logarithmic or exponential functions
depending on population size, number of islands, or other values, or using some statistical parameter setting method, such as Taguchi's \cite{Keratmatpour2018Taguchi}.

@@

This work has been partially funded by project SPIP2017-02116 (Spanish ``Direcci\'on General de Tr\'afico''), and projects EphemeCH TIN2014-56494-C4-3-P, TIN2015-67020-P, DeepBio TIN2017-85727-C4-2-P  and TEC2015-68752 (Spanish ``Ministerio de
Econom{\'ia}a y Competitividad'' and ERDF funds).
We would like to express our gratitude to the editorial team and the reviewers, whose valuable comments on this paper have significantly improved its quality.

>>>>

@@

%%%NEW AND SHORTED
Parallel island-model co-evolutionary algorithms are well-known methods, suitable for dealing with large multi-objective optimization problems. In these algorithms, each island modifies a fragment of the chromosome that encodes a possible solution to the problem. \textcolor{blue}{The objective of this paper is} to demonstrate that automatically setting the size of the overlapping fragments depending on the number of islands obtains better results than using the same size. \textcolor{blue}{This method has been compared} to other parallel evolutionary techniques considering a different number of islands, chromosome sizes and benchmarks. The analysis of the obtained experimental results, by using different metrics, shows that our approach can provide statistically significant improvements with respect to the base algorithm in high-dimensional, un-decomposable, multi-objective problems. This opens a very promising line to automatically adapt the overlapping sizes in this kind of algorithms.

@@

In our previous work \citep{Garcia16hpmoon} \textcolor{blue}{this method was used} in a
preliminary experimental setup, although it is worth mentioning \textcolor{blue}{that its name and acronym is established} in this paper for the first time.
\textcolor{blue}{It was shown}
that applying the variation operators only over specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
Moreover, instead of making every island focus on a disjoint subset of the
chromosome, the usage of overlapped (shared) sections of the
chromosome 
can improve the quality of the solutions 
when the number of islands is increased. In that paper, \textcolor{blue}{the results showed} that the most
adequate overlapping size may vary depending on a relation between the
number of islands and the individual size. However, it was a proof-of-concept, and the experiments
were conducted in a limited experimental system: mono-processor and
synchronous island model. 
This
motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more \textcolor{blue}{extensive parameter evaluation}. Besides comparing previous methods in this new experimental setup, in this paper 
a new method that automatically sets the size of the overlapped
sections depending on the number of available islands \textcolor{blue}{is proposed}, comparing it with previous versions.

@@

The approach described by Dorronsoro et al. has also been used by Kimovski et al. \citep{Kimovski15Parallel}, but implementing a
master-slave method that splits the population into several processors. As in previous works, each node
runs a parallel MOEA that only affects some portion of 
the individuals and the master
process receives all the sub-populations to be combined every certain number of generations. Up to 8 processors
were used in the experimental setup, and several
combination alternatives were compared. The main difference of our work with respect to previous works is that our approach does not 
broadcast all solutions to all islands for recombination, but only one solution to a random island, needing less
communication time. Moreover, Dorronsoro or Kimovsky approaches limited the maximum number of islands to 8, while in this paper \textcolor{blue}{up to 128 islands have been used}.

@@

In our previous work \citep{Garcia16hpmoon} some of
the aforementioned ideas \textcolor{blue}{were used} to compare two different dMOEAs. The first
one divided the chromosome into $P$ sections,  $P$ being the number of
islands. Every island $p$ only performed the mutation and crossover in
that part ($p_{th}$) of the chromosome (the selective operator application), while the fitness was
calculated using the whole individual. After a certain number of
generations, individuals were migrated randomly to other islands. The
performance metrics were calculated at the end of the run. The second
method, selective operator application with overlapping islands, used the $p_{th-1}$ and
$p_{th+1}$ sections of each chromosome, besides the $p_{th}$
part. During the same amount of time, both methods obtained better
results than a baseline algorithm that dealt with the whole chromosome
in each island for crossover and mutation. \textcolor{blue}{It was} discovered that the
performance using one or another method depends on the number of
sections of the individuals and the number of islands used. This
motivated us to find a new automatic method to select this number of
sections of the chromosome to use, depending on the number of
islands. Besides, previous experiments were performed on a single
processor synchronous island model with a limited number of islands
(8, 32 and 128). In this paper,  8, 16, 32, 64 and 128 islands have
been used, and on this occasion, the experiments have been run on a parallel
cluster. 
Therefore, at the same time, \textcolor{blue}{a new method is proposed in this paper} to divide the individual search space according to the number of evolved subpopulations, and also validating the previous approach.

%We will describe how we have tested our approach in the next Section.
\textcolor{blue}{The methodology to test our approach is described in the next Section.}

@@

The objective of this section is to explain the methodology followed to
compare the different versions of the overlapping schemes.

\subsection{Proposed methods}
In this paper \textcolor{blue}{several implemented SLA algorithms are analyzed}
 by using a parallel multi-objective baseline algorithm
as a basis for comparisons. Our proposed methods, using different overlapping schemes, 
are based on NSGA-II, as almost all the previous works discussed
before
\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Deb03distributed,Xiao03specialized,Wang09parallel,Martens13asynchronous}. 
Therefore, a basic distributed NSGA-II algorithm without
overlapping sections \textcolor{blue}{has been used} as the baseline (B).

This basic distributed algorithm spreads the population among $P$
islands; after a fixed number of generations,
one individual in a given island is migrated to another random island,
thus avoiding to synchronize the global PF every
certain number of generations as other methods described in Section 2
do. At the end of the run, the PFs of all islands are
aggregated into a new one, and the quality measures are evaluated. 
Different  SLA alternatives can be devised to evolve the
subpopulations according to the decision space to be explored by each
island. Here three methods \textcolor{blue}{will be considered} in which each island only
performs crossover and mutation in specific sections of the
individuals.

@@

The methods tested \textcolor{blue}{in this paper} are presented in the next subsections.

@@

As a first
approach to automatically calculate this value, the results shown in
\citep{Garcia16hpmoon} have been used as a base to obtain $c$. In that
work, the overlapped method ($c=1$) obtained better results when the
number of islands was bigger than 8. On the contrary, when the number of
islands is small, no overlapping is necessary. So, this
knowledge \textcolor{blue}{has been used} to propose the formula $c=round(0.2*P-1)/2$ to calculate the
extra sections to overlap. Therefore, when $P=8$ then $c=0$
(equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so
on. Dividing individuals by blocks of equal size, instead of a percentage, allow the future integration of our method with other recombination mechanisms, such as the ones presented in \cite{Dorronsoro13superlinear} or \cite{Kimovski15Parallel}.
Also, as mentioned, this is only a possible formula to reach above-described behaviour for $c$, and future work will study new methods or alternative formulas to determine it, for example using Taguchi Method \cite{Keratmatpour2018Taguchi}.  Figure \ref{fig:adaptive} explains the $A$ method, assuming that $c=2$, for example.

@@

Those metrics \textcolor{blue}{have been chosen} not only because they have been used
extensively, especially in some of the papers presented in Section \ref{sec:soa}
\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous},
but also because they cover different quality criteria. Mathematical
formulation of these metrics can be found in
\cite{Dorronsoro13superlinear}.

@@

The global population size is set to 1024. \textcolor{blue}{That value has been chosen} for two reasons: the first is that it is large enough to have 8 individuals per island by dividing that number when using 128 islands and small enough to have 128 individuals when using 8 islands. This is the minimum and maximum population size per island used by M{\"a}rtens et al. in his work \cite{Martens13asynchronous}.

The criterion used for terminating an experiment has been the running
time: 25 seconds for dimension 512 and 100s (four times more) for
2048. According to Alba and Luque \cite{EVALUATIONPARALLEL}, other stop criteria such as the number of evaluations required to attain a solution, may be misleading depending on the studied scenario. In our case, \textcolor{blue}{time has been used} instead of the number of evaluations firstly
because our hypothesis argues that the time saved in crossover and
mutation can be spent on improving the sub-populations and more
operations and migrations can be achieved. Also, 
different numbers of islands \textcolor{blue}{has been used} (with different sub-population sizes) and that
could lead to different execution times, so it would be difficult to
compare different times and quality of solutions at the same time.

The number of generations between migrations has been set to 5,
as
reported by \cite{Deb03distributed,Martens13asynchronous}. In general
and as affirmed by 
\cite{cantu1998survey}, this migration gap has contradictory effects
on the result: by increasing it, the system \textcolor{blue}{is made} closer to a
single-node one, since populations tend to mix without restriction; by
decreasing it, the isolate islands \textcolor{blue}{are} more prone to being stuck
in local minima. \cite{Martens13asynchronous} mentions that several
values were tested with no influence in the result; in our particular
case, the mixing is essential for the algorithm to spread the result
to all parts of the chromosome. So, while \textcolor{blue}{one might} tend to agree with
M{\"a}rtens on the small influence of this value on the result, \textcolor{blue}{it is possible} that making this value much bigger in our case would have a
negative impact. However, a precise fine-tuning of this value is left
as future work, as the main focus of this paper was to show the
general concept, and not tune the values for maximum performance.

@@

calculated (see Figure \ref{fig:hypervolume}), the value (1,9) \textcolor{blue}{has been chosen} as none of the existing solutions on all fronts obtained during all executions are dominated by it. In other words, as both objectives \textcolor{blue}{are being minimized}, this reference point is required to be numerically larger or equal in each objective, and strictly larger in at least one of them (dominated) for all solutions in the PFs \textcolor{blue}{used} to measure. HV is then

@@

The average results for each configuration are shown in
Table \ref{tab:results512} (for 512 dimensions) and Table
\ref{tab:results2048} (for 2048). As previously explained, when $P=8$
the results of A are equivalent to the obtained by D (because
$c=0$), and when $P=16$ they are equivalent to O ($c=1$). This equivalence \textcolor{blue}{is referred} with the word {\em Equiv-} in tables. For example, Equiv-D in an HV cell  means that the HV of A is the same than the value in D column, because the behaviour of this configuration is the same than executing D.

@@

%%%%%%FERGU: WARNING, THIS SECTION IS STILL SHIT
%ZDT1 
After establishing the performance of the new method and in order to
have some insight on how they work, the effect of the different chromosome sizes and number of
islands can be checked. Plotting the solution sets allows to observe its quality, distribution and shape, specially if they are limited to 2 or 3 objectives, as in this paper \cite{Li17read}.  Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048} show the
final PFs of one arbitrary sample run of each combination;. The first
one, ZDT1, has a convex Pareto-optimal front. Comparing results from
$L=512$ (Figure \ref{fig:plot_zdt1_512}) and $L=2048$ (Figure
\ref{fig:plot_zdt1_2048}) it is apparent that the quality of the
generated PFs depends on the chromosome size. Specifically, all
configurations  with
$L=512$  seem to have a worse Spread and HV, on the other hand, the
SLA methods behave worse than $B$, as it was also shown on average in
Table \ref{tab:results512}. Nevertheless, \textcolor{blue}{when focusing} on the plots
obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this
difference is less clear. Figure \ref{fig:plot_zdt1_2048} shows that
solutions obtained by the SLA methods show higher dispersion than the
baseline as $P$ grows. However, with $A$, the area covered by the PF
is still larger.

@@

In ZDT6, the Pareto-optimal solutions are not only non-uniformly distributed along the PF, but their density also increases \textcolor{blue}{when moving} further away from it. That is the reason why some PFs obtained have an extremely low number of solutions in some configurations, and also, they are aggregated toward the areas with more density. Moreover, all configurations, including $B$, obtained PFs relatively far away from the optimal PF, as opposed as in previous problems. Spread is very similar for all methods $B$, $D$, $O$, $A$ across different $L$ sizes. Indeed, there is not a significant difference between methods, with an exception: Spread using $A$ with $L=512$ is significantly worse. As in previous approaches, it is visually clear that increasing the number of islands, and therefore, reducing the number of individuals per island, implies a decrease the in quality of the HV.

@@

Obtained results also show that when increasing the number of islands, the
automatic overlapping method ($A$) significantly improves the results with
respect to the disjoint and overlapped methods. However, this is only
apparent with larger chromosome sizes. Therefore, the length of the
chromosome is also a key factor to take into account in automatic overlapping
methods, and not only the number of islands. 
%Studying this factor with more types of problems, and new configurations of population size and chromosome lengths could be addressed in the future. 
Since our method divides the individuals into blocks of divisible size, aggregation methods after migration, such as the ones used in \cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be also tested. But as complete individuals \textcolor{blue}{treated} in each island, the possibility of using a real number, such as 0.3 (30\% overlapping) instead an integer value opens future experimental setups.
For example, comparing 
different ways to calculate $c$ using linear, logarithmic or exponential functions
depending on population size, number of islands, or other values, or using some statistical parameter setting method, such as Taguchi's \cite{Keratmatpour2018Taguchi}.

@@

This work has been partially funded by project SPIP2017-02116 (Spanish ``Direcci\'on General de Tr\'afico''), and projects, TIN2015-67020-P, DeepBio TIN2017-85727-C4-2-P  and TEC2015-68752 (Spanish ``Ministerio de
Econom{\'ia}a y Competitividad'') and PGC2018-098813-B-C31 (Spanish ``Ministerio de Ciencia, Innovación y Universidades''), and by European Regional Development Funds (ERDF).
We would like to express our gratitude to the editorial team and the reviewers, whose valuable comments on this paper have significantly improved its quality.
